A Taxonomy of Twists of Supersymmetric Yang--Mills Theory

### 2020-01-31 paper.tex
4d (1,2) correction

\begin{prop}
Suppose $Q_t$ is the rank $(2,0)$ supercharge of \ref{eq:4dHodgefamily}.
The $\MU(2)$ decomposition of the functionals $I_{\rm gauge}^{(1)}, I^{(1)}_{\rm matter}, I^{(2)}_{\rm gauge}, I^{(2)}_{\rm matter}$ (see \eqref{eq:gaugeI1},  \eqref{eq:gaugeI2}, \eqref{eq:matterI1}, \eqref{eq:matterI2}) in terms of the fields of 4d $\cN=2$ super Yang--Mills theory are
\begin{align*}
I_{\rm gauge}^{(1)}(Q_t) &= \int \dvol\left(-(\rho, A_{1, 0}^*) - t(b, A_{0, 1}^*) - (\wt \chi + t\chi)\wt a^*\right) \\
& + \int\dvol\left((F_{0, 2}, B^*) + (\ol\dd_{A_{0, 1}}a, b^*) + \frac{1}{2}\Lambda(F_{1, 1}  + [a, \wt a])\chi^* + [\phi, \phi]\xi^* \right) \\
&+ \int\dvol\left( t\Omega^{-1} F_{2, 0}\wedge B^* + (t\dd_{A_{1, 0}} a, \rho^*)\right) \\
%&+ \int\dvol\left((F_{0, 2}, B^*) + t\Omega^{-1} F_{2, 0}\wedge B^* + (\ol\dd_{A_{0, 1}}a, b^*) + (t\dd_{A_{1, 0}} a, \rho^*) + \frac{1}{2}\Lambda F_{1, 1}(\chi^* - t\wt\chi^*)\right) \\
I^{(2)}_{\rm gauge} (Q_t, Q_t) &= \int \dvol \left(t\chi^*\wt \chi^* + \frac{t}{2} \xi^* B^* -\frac{1}{4}(\chi^* + t\wt\chi^*)^2 + t a c^*\right) \\
I_{\rm matter}^{(1)}(Q_t) &= \int \dvol \left((\Tilde{\nu}, \nu^*) + t (\varphi, \phi^*) + [\phi, \nu] + \frac{1}{2} (\dbar_{A_{0,1}} \phi, \psi^*) + [\nu, a]\varphi^* \right) \\
I_{\rm matter}^{(2)}(Q_t) &= \int \dvol \frac t4  (\psi^*, \psi^*)
\end{align*}
\end{prop}

@@

As a result of this argument, we are free -- as in the proof of Theorem \ref{thm:4dDonaldsontwist}, to set the eliminated fields $\chi, \wt \chi, \wt a, \nu, \wt \nu, \rho$ and $A_{1,0}$ to 0 in the twisted action functional.  This twisted action coincides with the sum of the $Q_0 + sQ_2$-twisted action functional from Theorem \ref{thm:4d_11_twist}, with the deformation by $tQ_1$, namely
\[\left(I^{(1)}(tQ_1) + 2 I^{(2)}(Q_0, tQ_1) + I^{(2)}(tQ_1, tQ_1)\right) + 2I^{(2)}(tQ_1, sQ_2).\]
The deformation given by the first three terms was computed in the proof of Theorem \ref{thm:4dDonaldsontwist} to be
\begin{equation}
\label{eq:4d_12_further_deformation}
t \int\dvol\left(-(b, A_{0, 1}^*) + a c^* + \frac{1}{2} \xi^* B^* + t (\varphi, \phi^*) + \frac 14 (\psi^*, \psi^*) \right).
\end{equation}
The fourth and final term, proportional to $st$, vanishes after the field elimination we have performed, since $\Gamma_{10}(Q_1,Q_2) = 0$, and the remaining term from equation \ref{eq:gaugeI2}, of form $st(Q_1,\lambda^*)(Q_2,\lambda^*)$, is proportional to $(Q_1,\lambda^*)$, which is proportional to $\chi^*$.

>>>>

\begin{prop}
\label{4d_donaldson_susy_prop}
Suppose $Q_t$ is the rank $(2,0)$ supercharge of \ref{eq:4dHodgefamily}.
The $\MU(2)$ decomposition of the functionals $I_{\rm gauge}^{(1)}, I^{(1)}_{\rm matter}, I^{(2)}_{\rm gauge}, I^{(2)}_{\rm matter}$ (see \eqref{eq:gaugeI1},  \eqref{eq:gaugeI2}, \eqref{eq:matterI1}, \eqref{eq:matterI2}) in terms of the fields of 4d $\cN=2$ super Yang--Mills theory are
\begin{align*}
I_{\rm gauge}^{(1)}(Q_t) &= \int \dvol\left(-(\rho, A_{1, 0}^*) - t(b, A_{0, 1}^*) - (\wt \chi + t\chi)\wt a^*\right) \\
& + \int\dvol\left((F_{0, 2}, B^*) + (\ol\dd_{A_{0, 1}}a, b^*) + \frac{1}{2}\Lambda(F_{1, 1}  + [a, \wt a])\chi^* + [\phi, \phi]\xi^* \right) \\
&+ \int\dvol\left( t\Omega^{-1} F_{2, 0}\wedge B^* + (t\dd_{A_{1, 0}} a, \rho^*)\right) \\
%&+ \int\dvol\left((F_{0, 2}, B^*) + t\Omega^{-1} F_{2, 0}\wedge B^* + (\ol\dd_{A_{0, 1}}a, b^*) + (t\dd_{A_{1, 0}} a, \rho^*) + \frac{1}{2}\Lambda F_{1, 1}(\chi^* - t\wt\chi^*)\right) \\
I^{(2)}_{\rm gauge} (Q_t, Q_t) &= \int \dvol \left(t\chi^*\wt \chi^* + \frac{t}{2} \xi^* B^* -\frac{1}{4}(\chi^* + t\wt\chi^*)^2 + t a c^*\right) \\
I_{\rm matter}^{(1)}(Q_t) &= \int \dvol \left((\Tilde{\nu}, \nu^*) + t (\varphi, \phi^*) + [\phi, \nu] + \frac{1}{2} (\dbar_{A_{0,1}} \phi, \psi^*) + [\nu, a]\varphi^* \right) \\
I_{\rm matter}^{(2)}(Q_t) &= \int \dvol \frac t4  (\psi^*, \psi^*)
\end{align*}
\end{prop}

@@

As a result of this argument, we are free -- as in the proof of Theorem \ref{thm:4dDonaldsontwist}, to set the eliminated fields $\chi, \wt\chi^*, \wt\chi + t\chi, \wt a, \wt a^*, \nu, \nu^*, \wt \nu, \wt \nu^* \rho, \rho^*, A_{1,0}$ and $A_{1,0}^*$ to 0 in the twisted action functional.  Finally, we set the remaining eliminated field $\chi^*-t\wt\chi^*$ equal to the expression $S_1$, as in Proposition \ref{prop:integrateoutfield}.  This twisted action coincides with the sum of the $Q_0 + sQ_2$-twisted action functional from Theorem \ref{thm:4d_11_twist}, with the deformation by $tQ_1$, namely
\begin{equation}
\label{eq:4d_12_general_def}
\left(I^{(1)}(tQ_1) + 2 I^{(2)}(Q_0, tQ_1) + I^{(2)}(tQ_1, tQ_1)\right) + 2I^{(2)}(tQ_1, sQ_2).
\end{equation}
To see this, we must verify that the expression $S_1$ occuring in the $Q_{st}$-twisted action functional agrees with the corresponding expression in the $Q_0 + sQ_2$-twisted action functional.  This follows from the fact that the only term proportional to $t(\chi^*-t\wt\chi^*)$ in the $Q_0 + tQ_1$-twisted action functional from equation \ref{4d_donaldson_susy_prop} is proportional to $\wt \chi^*$, and so vanishes after setting $\wt \chi^* = 0$.

The deformation given by the first three terms in \ref{eq:4d_12_general_def} was computed in the proof of Theorem \ref{thm:4dDonaldsontwist} to be
\begin{equation}
\label{eq:4d_12_further_deformation}
t \int\dvol\left(-(b, A_{0, 1}^*) + a c^* + \frac{1}{2} \xi^* B^* + t (\varphi, \phi^*) + \frac 14 (\psi^*, \psi^*) \right).
\end{equation}
The fourth and final term, proportional to $st$, vanishes after the field elimination we have performed, since $\Gamma_{10}(Q_1,Q_2) = 0$, and the remaining term from equation \ref{eq:gaugeI2}, of form $st(Q_1,\lambda^*)(Q_2,\lambda^*)$, is proportional to $(Q_1,\lambda^*)$, which is proportional to $\chi^*$.
